Computer Science House Constitution

### 2013-05-24 constitution.tex
Fixed date, and allowed for cross-document hyperlinking

% Define the external document to be bylaws for cross referencing purposes
\externaldocument{bylaws}

% Title page information
\title{Computer Science House Constitution}
\author{Computer Science House Executive Board}
% Last Modified Date
\newcommand{\datechanged}{Proposed: \today}
\date{\datechanged}

@@

% Headings
\pagestyle{myheadings}
\markright{{\rm CSH Constitution \hfill  As of \datechanged \hfill Page }}

@@

% Articles
\article{Name}
The name of this Special Interest House shall be Computer Science House.

\article{Derivation of Authority}
The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Department of Residence Life in conjunction with the Residence Halls Association.

\article{House Objectives}
The objectives of Computer Science House are:
	\begin{enumerate}
	\item To enhance the education experience of its members.
	\item To offer students educational programming with an emphasis in computers.
	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community.
	\item To provide a friendly and comfortable living environment in the residence halls.
\end{enumerate}

\article{Constitutional Structure}
\asection{House Charter}
The House Charter is a document drafted by the department of Residence Life, setting down the guidelines within which this House operates and from which it derives its authority.

\asection{Constitution}
The House Constitution is written and maintained by the House and defines the major aspects, goals, and governing structure of the house.  It is reviewed annually by the Department of Residence Life.  The House Constitution is comprised of three sections:  articles, by-laws, and guidelines.  Any non-semantic change to an article or by-law should be presented to the House by the Evaluations Committee for discussion.  After the discussion an immediate House vote is taken.  A quorum of fifty percent of the number of all House members eligible to vote must be present in order for the vote to be official.  A vote exceeding fifty percent of all House members casting a vote is required for the non-semantic change to be placed into the constitution.  Non-semantic changes to the guidelines and semantic changes to articles, by-laws, or guidelines are described in detail below.

\asubsection{Articles}
Articles define the major aspects of the House. Any semantic change to an article requires the change to be proposed in writing for discussion at a House Meeting. Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week. The final proposal is presented the following week and ballots are distributed for a secret ballot House vote as described in \ref{Voting}, Voting. The ballots are collected for a minimum of a forty-eight hour period. A quorum of two-thirds of the number of all House members eligible to vote must cast ballots for the vote to be official. A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution. An article may be overridden by an immediate House vote as described in \ref{Voting}, Voting. There must be a quorum of eighty-five percent of the number of all House members eligible to vote for the vote to be official. A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.

\asubsection{By-Laws}
By-Laws define the more flexible aspects of the House. A by-law may expand on rules outlined in an article, but they must never contradict an article. Any semantic change to a by-law requires the change to be proposed in writing for discussion at a House Meeting. Any modifications made due to the discussion are added to the written proposal and the modified proposal is re-read prior to voting. The vote may be taken immediately or tabled one week at the discretion of the Executive Board. When the final proposal is ready to be voted upon, an immediate House vote will be taken as described in \ref{Voting}, Voting. A quorum of two-thirds of the number of all House members eligible to vote must cast a vote for the vote to be official. A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution. A by-law may be overridden by an immediate House vote as described in \ref{Voting}, Voting. There must be a quorum of two-thirds of the number of all House members eligible to vote for the vote to be official. A vote equaling or exceeding two-thirds of the number of votes cast is required for the override to take effect.

\asubsection{Guidelines}
Guidelines define the standard operating procedure of the Committees of the House. Guidelines must never contradict any rule defined in either the articles or by-laws. They are drafted during the Executive Board Training Process by the Director of the respective Committee. Directors and Committees are expected to adhere to them, but if necessary, may deviate from a stated guideline. The guidelines will include:
\begin{itemize}
\item An explicit definition of what it means to be a member of the respective committee
\item Expectations of members in the committee
\item Goals of the committee for the operating year
\end{itemize}
The House must be notified of any deviation from a stated guideline. Any semantic or non-semantic change to a guideline is presented in writing to the Committee the guideline pertains to. The change must pass a simple majority vote within the members of the committee for it to be accepted. It is then presented to the Executive Board for review prior to placing it in the Constitution. The House is notified of the change at the following House meeting.

\asubsection{House Rules}
The House Rules capsulate a House Member's responsibilities and expectations. Members are required to sign the document signifying their acceptance of the membership requirements and expectations. All Resident and Non-Resident are required to sign the House Rules annually. Because the House Rules are extracted from the Constitution, any modifications to the contents of the House Rules must first be made to the Constitution. \ref{Operations of the Executive Board}, \ref{The House Rules}, describes which information is extracted from the Constitution and placed into the House Rules.

\article{Membership}
There are six major types of membership available to Computer Science House.  Each carries different qualifications, expectations, and privileges.  When describing the different memberships available, the following terms are used:
\begin{description}
\item[Qualifications:] What qualifications an applicant needs to apply.
\item[Selection:] The process by which an applicant gains membership.
\item[Expectations:] What expectations the House has on its members.
\item[Privileges:] What privileges the member can expect from the House.
\item[Evaluations:] The process by which a member is reviewed and evaluated.
\item[Resignations:] The process by which a member resigns membership.
\item[Term:] The length of time the membership lasts.
\end{description}
\asection{Introductory Membership}
\asubsection{Introductory Membership Qualifications}
Introductory Membership is open to all RIT students.
\asubsection{Introductory Membership Selection}
Applicants notify the House of their interest in membership by submitting an application to the Evaluations Committee.  They must then undergo the selection process as defined in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Students Attending RIT for at Least One Quarter} and \ref{Selection Process for First Quarter and Entering RIT Students}.
\asubsection{Introductory Membership Expectations}
Introductory members are expected to be active participants in the House as defined in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}. If an Introductory member fails to  obtain 60\% (rounded up to the nearest whole person) of the Resident  Members signatures in the Introductory packet, discussed in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}, said member will not receive use of Computer Science House  facilities, as described in \ref{Introductory Membership Privileges}, until successful completion  of Introductory Evaluations.
\asubsection{Introductory Membership Privileges}
Introductory members receive the right to use Computer Science House facilities, to attend House functions, and to have housing priority over all persons who are not Computer Science House members.
\asubsection{Introductory Membership Evaluations}
Introductory members are evaluated on their performance during the introductory period.  The introductory process is described in \ref{Operations of the Evaluations Committee}, \ref{The Introductory Process}.
\asubsection{Introductory Membership Resignations}
An introductory member may resign by submitting the request for termination of membership to the House Chairman, or Evaluations Director in writing before the completion of the introductory process.
\asubsection{Introductory Membership Term}
The introductory membership shall last until the end of the introductory process, at which time they will either have their membership revoked or have their membership status changed to Resident member or Non-Resident member.

\asection{Resident Membership}
\asubsection{Resident Membership Qualifications}
Resident Membership is open to all RIT students who comply with the Residence Life policies regarding residence in the Residence Halls.
\asubsection{Resident Membership Selection}
Applicants notify the House of their interest in Resident Membership by submitting an application to the Evaluations Committee and must then undergo the Selection Process as described in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Students Attending RIT for at Least One Quarter} and \ref{Selection Process for First Quarter and Entering RIT Students}.
\asubsection{Resident Membership Expectations}
Resident members are expected to live on the house and be active participants in the House as defined in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}.
\asubsection{Resident Membership Privileges}
Resident Members receive the right: to vote on all issues brought before the House, to have residency on the House, to hold an Executive Board office on the House, to use the Computer Science House facilities, to attend Computer Science House functions, to have priority for available housing on the House when returning from cooperative education as stated in \ref{Operations of the Evaluations Committee}, \ref{Housing Priority System}, to have guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process.
\asubsection{Resident Membership Evaluations}
Resident Members are evaluated semi-annually through the Evaluation Process as described in \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.  Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Resident Membership Resignations}
A Resident member may resign by submitting in writing the reason for resignation to the House Chairman, or Evaluations Director.  The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Resident Membership Term}
Resident Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.

\asection{Non-Resident Membership}
\asubsection{Non-Resident Membership Qualifications}
Non-Resident membership is open to all RIT students.
\asubsection{Non-Resident Membership Selection}
Applicants notify the House of their interest in Non-Resident membership by submitting an application to the Evaluations Committee and must then undergo the Selection Process as described in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Students Attending RIT for at Least One Quarter} and \ref{Selection Process for First Quarter and Entering RIT Students}.  Any house Alumni may become a Non-Resident member by notifying the Evaluations Committee of their intent to participate, at which point they are reinstated as Non-Resident members of the house.
\asubsection{Non-Resident Membership Expectations}
Non-Resident members are expected to be active participants in the House as defined in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}.
\asubsection{Non-Resident Membership Privileges}
Non-Resident Members receive the right: to vote on all issues brought before the House, to use the Computer Science House facilities, to attend Computer Science House functions, to have priority for available housing on the House as stated in \ref{Operations of the Evaluations Committee}, \ref{Housing Priority System}.
\asubsection{Non-Resident Membership Evaluations}
Non-Resident Members are evaluated semi-annually through the Evaluation Process as described in \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.
\asubsection{Non-Resident Membership Resignations}
A Non-Resident Member may resign by submitting in writing the reason for resignation to the House Chairman, or Evaluations Director.  The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Non-Resident Membership Term}
Non-Resident Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status according to \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.

\asection{Alumni Membership}
\asubsection{Alumni Membership Qualifications}
Alumni Membership is open to all prior members of Computer Science House who departed for reasons other than revocation of House Membership or failing the Objective Evaluation. 
\asubsection{Alumni Membership Selection}
Alumni Membership is the status of all prior members of Computer Science House who departed the house for any reasons other than failure of the Evaluations Process as described in \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.
\asubsection{Alumni Membership Expectations}
There are no expectations associated with the Alumni Membership status, however those who are able are encouraged to adhere to \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}.
\asubsection{Alumni Membership Privileges}
Alumni Members, at the discretion of the Executive Board, shall receive the right: to the use of Computer Science House facilities and to attend Computer Science House functions.
\asubsection{Alumni Membership Evaluations}
Alumni Members are not subject to the Evaluations Process.
\asubsection{Alumni Membership Resignations}
There are no resignations associated with Alumni Membership status.
\asubsection{Alumni Membership Term}
Alumni Membership shall last until the member changes their membership status as described in the Qualifications and Selections sections of either Resident or Non-Resident Membership.

\asection{Honorary Membership}
\asubsection{Honorary Membership Qualifications}
Honorary Membership is open to a person whom the House feels has contributed great personal effort to the House and is deserving of House recognition.
\asubsection{Honorary Membership Selection}
Any House member may nominate a candidate for Honorary Membership by submitting the name in writing to the Evaluations Committee. The Evaluation Committee then begins the Honorary Membership Selection Process as defined in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Honorary Members}.
\asubsection{Honorary Membership Expectations}
Honorary Members are encouraged to remain in contact with the House.
\asubsection{Honorary Membership Privileges}
Honorary Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
\asubsection{Honorary Membership Evaluations}
Honorary Members are not subject to formal evaluations.
\asubsection{Honorary Membership Resignations}
An Honorary Member may resign by submitting in writing the reason for resignation to the House Chairman. The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Honorary Membership Term}
Honorary Membership shall last until the member resigns.

\asection{Advisory Membership}
\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
\asubsection{Advisory Membership Selection}
Advisors are selected during the start of the academic year. Any House member may nominate a candidate for Advisory Membership by submitting the name in writing to the Executive Board. The candidates then participate in the Advisor Selection Process as defined in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Advisory Members}.
\asubsection{Advisory Membership Expectations}
Advisors are encouraged to offer advise and assistance to the House in any capacity the Advisor is able to help. Advisors are also encouraged to meet the House members and occasionally attend House activities.
\asubsection{Advisory Membership Privileges}
Advisory Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
\asubsection{Advisory Membership Evaluations}
Advisors are not subject to formal evaluations.
\asubsection{Advisory Membership Resignations}
An Advisor may resign by submitting in writing the reason for resignation to the House Chairman. The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Advisory Membership Term}
Advisory Membership shall last for one academic year or until the member resigns.

\article{Executive Board}
The Executive Board is the main governing body of the House.  Its purpose if to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
\asection{Members of the Executive Board}
\asubsection{Chairman}
\asubsection{Voting Members}
\begin{itemize}
    \item Evaluations Director
    \item Social Director(s)
    \item Financial Director
    \item Research and Development Director
    \item House Improvements Director
    \item Root Type Persons Representative
    \item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
    \item House Secretary
\end{itemize}

\asection{Responsibilities}
% For this section, we want items to use letters
\renewcommand{\theenumi}{\alph{enumi}}
\asubsection{Responsibilities of the Executive Board}
\begin{enumerate}
\item To fulfill the responsibilities pertaining to its purpose as stated in the description of the Executive Board in the header paragraph for \ref{Executive Board} (Executive Board).
\item To meet at least weekly during the standard operating session, as defined in \ref{General Operations of the House}, \ref{Standard Operating Session}, to discuss and report the operations of the House.
\item To report pertinent information to House members at the following House Meeting.
\item To establish goals and expectations for the House for the upcoming year.
\item To submit a yearly statement of goals and accomplishments of the present year to House members and to the Department of Residence Life.
\item To act as a judicial board for any final ruling on the interpretation of the House Constitution, House document, or action taken by the House.
\end{enumerate}

\asubsection{Responsibilities of the Chairman}
\begin{enumerate}
\item To preside over Executive Board and House Meetings.
\item To exercise general supervision over the operations of the Executive Board.
\item To exercise general supervision over regular House activities.
\item To act as a liaison to the academic and administrative departments at RIT.
\item To act in collaboration with the Evaluations Director and an additional Executive Board member who is chosen by a simple majority vote among the members of the Executive board as a judicial board for any initial ruling on the interpretation of the House Constitution, House document, or action taken by the House. 
\item To cast tie-breaking vote in a split decision in an Executive Board vote.
\end{enumerate}

\asubsection{Responsibilities of the Evaluations Director}
\begin{enumerate}
\item To preside over Evaluations Committee Meetings
\item To exercise general supervision over the operations of the Evaluations Committee.
\item To oversee the selection of new House members.
\item To oversee the evaluations of current House members.
\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership status to Resident Membership.
\item To act in collaboration with the Chairman and an additional Executive Board member who is chosen by a simple majority vote among the members of the Executive board as a judicial board for any initial ruling on the interpretation of the House Constitution, House document, or action taken by the House. 
\item To prepare the House for Open Houses, tours, and special events.
\end{enumerate}

\asubsection{Responsibilities of the Social Director}
\begin{enumerate}
\item To preside over Social Committee Meetings
\item To exercise general supervision over the operations of the Social Committee.
\item To oversee the organization, initiation, and execution of House activities and events.
\end{enumerate}
\asubsection{Responsibilities of the Financial Director}
\begin{enumerate}
\item To oversee the Financial Committee.
\item To supervise financial administrators and transactions involving house projects.
\item To maintain financial and inventory records of House capital and assets.
\item To plan and enforce a House budget.
\item To supervise House expenditures and financial transactions.
\item To publish a quarterly House financial statement.
\item To supervise the collection of quarterly House dues.
\item To oversee the planning and execution of fundraising events.
\end{enumerate}

\asubsection{Responsibilities of the Research and Development Director}
\begin{enumerate}
\item To preside over Research and Development Committee Meetings
\item To exercise general supervision over the operations of the Research and Development Committee.
\item To oversee the organization and construction of technical projects for the House's benefit.
\item To collaborate with the Operational Communications Committee in an attempt to fulfill the House's need for technical equipment.
\item To provide seminars and tutorials to educate House members in technical areas.
\end{enumerate}

\asubsection{Responsibilities of the House Improvements Director}
\begin{enumerate}
\item To preside over House Improvements Committee Meetings.
\item To exercise general supervision over the operations of the House Improvements Committee.
\item To oversee the organization and construction of physical improvements to the House.
\item To oversee the general maintenance of the appearance of the House.
\end{enumerate}

\asubsection{Responsibilities of the Root Type Persons Representative}
\begin{enumerate}
\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings.
\item To report the status of the House computer systems and network to the Executive Board and House members.
\item To oversee the implementation of maintenance and upgrades to the House Computer Systems and Network.
\end{enumerate}

\asubsection{Responsibilities of the Root Type Persons}
\begin{enumerate}
\item The Root Type Persons are responsible for improvement, maintenance, and management of the House's computer systems and networking equipment.
\item There must always be at least two Root Type Persons at all times.
\end{enumerate}

\asubsection{Responsibilities of the House History Director}
\begin{enumerate}
\item To preside over House History Committee Meetings
\item To exercise general supervision over the operations of the House History Committee.
\item To oversee the upkeep of House Members records.
\item To oversee the celebration of all House Member's birthdays.
\item To oversee the production of a quarterly newsletter highlighting Computer Science House happenings and a yearly Alumni Directory.
\item To maintain, uphold, and promote house traditions.
\item To collaborate with the Social Director(s) to ensure that all the Non-Resident, Alumni, and Advisory Members are informed of upcoming events.
\end{enumerate}

@@

\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated. The vacated office is then handled like any other vacated office; see \ref{Executive Board}, \ref{Resignations}.

@@

\item When attendance requirements call for the Social Directors to be present, both dual directorship members are to fulfill the requirements.

@@

\asubsection{Selection of Root Type Persons}

>>>>

% Define the external document to be bylaws for cross referencing purposes
\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]

% Title page information
\title{Computer Science House Constitution}
\author{Computer Science House Constitution Committee}
% Last Modified Date
\newcommand{\datechanged}{Proposed: \today}
\date{\datechanged}

@@

% % Adding an \asubsubsection -- I feel dirty
\setcounter{secnumdepth}{5}
\newcommand{\asubsubsection}[1]{\paragraph{#1} \label{#1}}
\renewcommand{\theparagraph}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}}

% Headings
\pagestyle{myheadings}
\markright{{\rm CSH Constitution \hfill \datechanged \hfill Page }}

@@

% ARTICLE I - INTRODUCTION
\article{Introduction}

\asection{Name}
The name of this Special Interest House shall be Computer Science House.

\asection{Derivation of Authority}
The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Department of Residence Life in conjunction with the Residence Halls Association.

\asection{House Objectives}
The objectives of Computer Science House are:
\begin{enumerate}
	\item To enhance the education experience of its members.
	\item To offer students educational programming with an emphasis in computers.
	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community.
	\item To provide a friendly and comfortable living environment in the residence halls.
\end{enumerate}

% ARTICLE II - CONSTITUTIONAL STRUCTURE
\article{Constitutional Structure}

\asection{House Charter}
The House Charter is a document drafted by the department of Residence Life, setting down the guidelines within which this House operates and from which it derives its authority.

\asection{Constitution}
The House Constitution is written and maintained by the House and defines the major aspects, goals, and governing structure of the house. It is reviewed annually by the Department of Residence Life. The House Constitution is comprised of two sections: articles and by-laws. Articles define the major aspects of the House. A by-law may expand on rules outlined in an article, but they must never contradict a Constitutional article.

\asubsection{ Non-Semantic Changes}
Any non-semantic change to the Constitution should be presented to the House for discussion. After the discussion an immediate House vote is taken. A quorum of fifty percent of the number of all House members eligible to vote must be present in order for the vote to be official. A vote exceeding fifty percent of all House members casting a vote is required for the non-semantic change to be placed into the constitution.

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting. Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week. The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}. The ballots are collected for a minimum of a forty-eight hour period. A quorum of two-thirds of the number of all House members eligible to vote must cast ballots for the vote to be official. A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution. The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}. There must be a quorum of eighty-five percent of the number of all House members eligible to vote for the vote to be official. A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.

% ARTICLE III - MEMBERSHIP
\article{Membership}
There are five major types of membership available to Computer Science House. Each carries different qualifications, expectations, and privileges. When describing the different memberships available, the following terms are used:
\begin{description}
	\item[Qualifications:] What qualifications an applicant needs to apply.
	\item[Selection:] The process by which an applicant gains membership.
	\item[Expectations:] The duties and responsibilities of House members.
	\item[Privileges:] The benefits offered to House members.
	\item[Evaluations:] The process by which a member is reviewed and assessed.
	\item[Resignations:] The process by which a member terminates House membership.
	\item[Term:] The length of time the membership lasts.
\end{description}

\asection{Introductory Membership}
\asubsection{Introductory Membership Qualifications}
Introductory Membership is open to all students at the Rochester Institute of Technology.
\asubsection{Introductory Membership Selection}
Applicants notify the House of their interest in membership by submitting an application to the Evaluations Director. They must then undergo the selection process as defined in \ref{Selection Processes}.
\asubsection{Introductory Membership Expectations}
Introductory members are expected to meet all the requirements of the Introductory Process, as described in \ref{Expectations of an Introductory Member}.
\asubsection{Introductory Membership Privileges}
Introductory members receive the right to use Computer Science House facilities, to attend House functions, and to have housing priority over all persons who are not Computer Science House members.
\asubsection{Introductory Membership Evaluations}
Introductory members are evaluated on their performance during the introductory period. The introductory evaluation process is described in \ref{Introductory Evaluation}.
\asubsection{Introductory Membership Resignations}
Introductory members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
\asubsection{Introductory Membership Term}
Introductory membership shall last until the end of the introductory process, at which time active membership is granted or membership is revoked.

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and the most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting. If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately. The decision will be announced at the following House meeting.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
\asubsection{Active Membership Evaluations}
Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.  Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Active Membership Resignations}
A Active member may resign by submitting in writing the reason for resignation to the Chairman, or Evaluations Director.  The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.

\asection{Alumni Membership}
\asubsection{Alumni Membership Qualifications}
Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evaluation and departed for reasons other than revocation of House Membership.
\asubsection{Alumni Membership Selection}
Alumni who depart house for any reasons other than failure of the Membership Evaluation process, are considered to be in good standing. All other alumni are considered to be in bad standing.
\\*\\*
Active members who depart house prior to the Membership evaluation will be an alumni in bad standing. The member may appeal to EBoard for an exemption based on their circumstances. 
\asubsection{Alumni Membership Expectations}
There are no expectations associated with the Alumni Membership status.
\asubsection{Alumni Membership Privileges}
Alumni Members shall receive the right to:
\begin{itemize}
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
\end{itemize}
\asubsection{Alumni Membership Evaluations}
Alumni Members are not subject any evaluation.
\asubsection{Alumni Membership Resignations}
There are no resignations associated with Alumni Membership status.
\asubsection{Alumni Membership Term}
Alumni Membership shall last indefinitely or until the member chooses to pursue Active Membership.

\asection{Honorary Membership}
\asubsection{Honorary Membership Qualifications}
Honorary Membership is open to a person whom the House feels has contributed great personal effort to the House and is deserving of House recognition.
\asubsection{Honorary Membership Selection}
Any House member may nominate a candidate for Honorary Membership by submitting the name in writing to the Evaluations Director. The Evaluation Director then begins the Honorary Membership Selection Process as defined in \ref{Selection Process for Honorary Members}
\asubsection{Honorary Membership Expectations}
Honorary Members are encouraged to remain in contact with the House.
\asubsection{Honorary Membership Privileges}
Honorary Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
\asubsection{Honorary Membership Evaluations}
Honorary Members are not subject to formal evaluations.
\asubsection{Honorary Membership Resignations}
An Honorary Member may resign by submitting in writing the reason for resignation to the Chairman. The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Honorary Membership Term}
Honorary Membership shall last until the member resigns.

\asection{Advisory Membership}
\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
\asubsection{Advisory Membership Selection}
The Executive Board may open nominations for Advisory Members. The candidates then participate in the Advisory Selection Process as defined in \ref{Selection Process for Advisory Members}
\asubsection{Advisory Membership Expectations}
Advisors are encouraged to offer advice and assistance to the House in any capacity the Advisor is able to help. Advisors are also encouraged to meet the House members and occasionally attend House activities.
\asubsection{Advisory Membership Privileges}
Advisory Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
\asubsection{Advisory Membership Evaluations}
Advisors are not subject to formal evaluations.
\asubsection{Advisory Membership Resignations}
An Advisor may resign by submitting in writing the reason for resignation to the Chairman. The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Advisory Membership Term}
Advisory Membership shall last until the member resigns.

% ARTICLE IV - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House. Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House. It is composed of the seven permanent directors and the Chairman.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member. Ad-hoc directorships are created on an as-needed basis. They are generally very task oriented and are chaired by a House member. A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest. Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Chairman}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director
	\item House Improvements Director
	\item Operational Communications Director
	\item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item House Secretary
	\item Ad Hoc Directors
\end{itemize}
\asection{Closed Executive Board}
Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board. A closed Executive Board meeting may be called at any time by any member of the Executive Board. However, the Chairman and at least two-thirds of the Voting Members must be present for the meeting to be called.

\asection{Responsibilities}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\asubsection{Responsibilities of the Executive Board}
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House.
	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House.
	\item To report pertinent information to House members at the following House Meeting.
	\item To maintain records of the goals defined by each previous Executive Board.
	\item To act as a Judicial Board as defined in \ref{Judicial}.
	\item To review major projects, as defined in \ref{Expectations of House Members},  presented to them by the Evaluations director.
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.
	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.The constitution should remain up to date with current practices.
\end{enumerate}

\asubsection{Responsibilities of the Chairman}
\begin{enumerate}
	\item To preside over Executive Board and House Meetings.
	\item To exercise general supervision over the operations of the Executive Board.
	\item To exercise general supervision over regular House activities.
	\item To act as a liaison to the academic and administrative departments at RIT.
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
	\item To cast tie-breaking vote in a split decision in an Executive Board vote.
\end{enumerate}

\asubsection{Responsibilities of the Evaluations Director}
\begin{enumerate}
	\item To preside over Evaluations Meetings.
	\item To exercise general supervision over Evaluations operations.
	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members.
	\item To oversee the Semi-Annual Evaluations of current House members.
	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency.
	\item To act in collaboration with the Chairman and an additional Executive Board member who is chosen by a simple majority vote among the members of the Executive board as a judicial board for any initial ruling on the interpretation of the House Constitution, House document, or action taken by the House. 
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
	\item To prepare the House for Open Houses, tours, and special events.
\end{enumerate}

\asubsection{Responsibilities of the Social Director}
\begin{enumerate}
	\item To preside over Social Meetings. House members are encouraged to bring ideas for social events to the meetings for discussion.
	\item To exercise general supervision over Social operations.
	\item To oversee the organization, initiation, and execution of House activities and events.
	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year.
\end{enumerate}

\asubsection{Responsibilities of the Financial Director}
\begin{enumerate}
	\item To preside over Financial Meetings. House members are encouraged to bring ideas for fund-raising activities to the meetings for discussion.
	\item To supervise financial administrators and transactions involving house projects.
	\item To maintain financial and inventory records of House capital and assets.
	\item To plan and enforce a House budget.
	\item To oversee House finances and generation of House funds.
	\item To publish a semesterly House financial statement.
	\item To supervise the collection of semesterly House dues.
	\item To oversee the planning and execution of fundraising events.
\end{enumerate}

\asubsection{Responsibilities of the Research and Development Director}
\begin{enumerate}
	\item To preside over Research and Development Meetings. House members are encouraged to bring ideas for projects to the meetings for discussion.
	\item To exercise general supervision over Research and Development operations.
	\item To oversee the planning, organization and construction of technical projects for the House's benefit.
	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment.
	\item To provide seminars and tutorials to educate House members in technical areas.
\end{enumerate}

\asubsection{Responsibilities of the House Improvements Director}
\begin{enumerate}
	\item To preside over House Improvements Meetings.
	\item To exercise general supervision over the House Improvements operations.
	\item To oversee the organization and construction of physical improvements to the House.
	\item To oversee the general maintenance of the appearance of the House.
\end{enumerate}

\asubsection{Responsibilities of the Operational Communications Director}
\begin{enumerate}
	\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings.
	\item To report the status of the House computer systems and network to the Executive Board and House members.
\end{enumerate}

\asubsection{Responsibilities of the House History Director}
\begin{enumerate}
	\item To preside over House History Meetings.
	\item To exercise general supervision over the House History operations.
	\item To maintain, uphold, and promote house traditions.
	\item To collaborate with the Social Director(s) to ensure that all the Active, Alumni, and Advisory Members are informed of upcoming events.
	\item To oversee the production and distribution of a semi-annual newsletter.
	\item To oversee the creation of a yearbook outlining House events for the year.
\end{enumerate}

@@

	\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated. The vacated office is then handled like any other vacated office; see \ref{Resignations}.

@@

	\item When attendance requirements call for the dual directorship position to be present, both dual directorship members are to fulfill the requirements.

@@

\asubsection{Selection of Ad Hoc Directors}
